---
title: "DSA2101 Group Project: Analysis of Taylor Swift Spotify Data"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidytuesdayR)
library(tidyverse)
library(readr)
library(knitr)
library(ggthemes)
library(ggridges)
```

## Group members
```{r, echo = FALSE}
students <- data.frame(
  Group_Members = c("Chua Yong Sheng Joel", "Lim Zeen Kiat", "Robin Ghosh", "Timothy Teo Shao Jun"),
  Matriculation_Number = c("A0282307H", "A0273151M", "A0271671A", "A0272851B")
)

kable(students, col.names = c("Names", "Matriculation Number"))
```

## Loading the Taylor Swift Datasets
```{r}
tuesdata <- tidytuesdayR::tt_load(2023, week = 42)

taylor_album_songs <- tuesdata$taylor_album_songs
taylor_all_songs <- tuesdata$taylor_all_songs
taylor_albums <- tuesdata$taylor_albums
```
==============================

## 1. Introduction

Taylor Swift's music has had a significant impact on the global pop and country music scene. 
In this project, we used the Taylor Swift Spotify data sourced from the TidyTuesday repository (Harmon, 2023) to analyse the musical and lyrical features of her music. 
This dataset includes detailed audio attributes of her songs which we aim to use. 
By exploring the given data, we aim to discover the patterns that have emerged throughout Taylor Swift’s career and gain insights into how her music has evolved.


### Brief description of the Dataset
`taylor_album_songs` ~ Song features and *metadata* for only songs released in albums.

`taylor_all_songs` ~ Song features and *metadata* for all songs released by Artist

`taylor_albums` ~ *Metadata* for each album, together with Metacritic and User Scores (Used as receptivity metrics).

* **Metadata** refers to technical aspects of the release like track name, track number and release dates.
* Download dataset from: https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-10-17/readme.md

For our project, we aim to answer the following question:

```bash
How have differences in musical and lyrical features in Taylor Swift's songs resonated with her audience?
```
This analysis will allow us to identify trends in musical characteristics and examine how stylistic changes in her songs which have affected the receptivity of her music to her audience, meaning how much they like her songs. 
We also hope to understand her audience better by knowing their music preferences through this study. Hence, we can perhaps understand what makes Taylor Swift so popular.


## 2. Data Cleaning & Summary

### Summary of relevant statistics
The following table contains a brief description of the variables we have chosen to use for our project (Harmon, 2023):
These features will enable us to compare the songs' descriptive features through a quantitative lense, allowing us to make judgements backed by figures. 
```{r, echo = FALSE}
track_attributes <- data.frame(
  Variable = c(
    "album_name", "album_release", "track_name", "danceability", "energy",
    "loudness", "mode", "speechiness", "acousticness", "instrumentalness",
    "liveness", "valence", "tempo", "explicit", "Metacritic Score", "User Score"
  ),
  Class = c(
    "character", "double", "character", "double", "double", "double", "integer",
    "double", "double", "double", "double", "double", "double", "logical", "double", "double"
  ),
  Description = c(
    "Name of the album the track belongs to.",
    "Release date of the album.",
    "Name of the individual track.",
    "Measures how suitable a track is for dancing.",
    "Measures the intensity and activity of a track, with higher values indicating more energetic sounds.",
    "The overall volume of the track, measured in decibels (dB).",
    "This is a categorical variable. It indicates the modality of the track: 1 for major, 0 for minor.",
    "Measures the presence of spoken words in a track, with higher values indicating more speech-like content.",
    "Represents the likelihood that the track is acoustic, with higher values indicating more acoustic qualities.",
    "Predicts whether a track is instrumental, with higher values suggesting a lack of vocals.",
    "Measures the presence of an audience in the recording, with higher values indicating a stronger likelihood that the track is live",
    "Describes the musical positiveness conveyed, with higher values indicating more cheerful and happy tones.",
    "The speed of the track, measured in beats per minute (BPM).",
    "Indicates whether the track contains explicit content: 1 for explicit, 0 otherwise.",
    "Average score of the album obtained from critics at Metacritic.com",
    "Average score of the album obtained from average users at Meatcritic.com"
  )
)
kable(track_attributes, col.names = c("Variable", "Class", "Description"), align = "l")
```

### Data cleaning
We'll start off by filtering for the features listed above. We do not need the "EP" flag as well
because we are interested in **all** the songs in her albums which are present in `taylor_albums`. 
```{r}
taylor_album_songs <- taylor_album_songs %>%
  select(album_name, album_release, track_number, track_name, danceability, energy, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, explicit)

taylor_all_songs <- taylor_all_songs %>%
  select(album_name, album_release, track_number, track_name, danceability, energy, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, explicit)

taylor_albums <- taylor_albums %>%
  select(!ep)
```

Then, we group the data by their **respective albums** for aggregating album data:
```{r}
taylor_album_songs <- taylor_album_songs %>%
  group_by(album_name)

taylor_all_songs <- taylor_all_songs %>%
  group_by(album_name)

taylor_albums <- taylor_albums %>%
  group_by(album_name)
```

We will check and remove NA values in the data, which are not needed for our visualisations:
```{r}
taylor_album_songs_na_count <- sapply(taylor_album_songs, function(x) sum(is.na(x)))
print(taylor_album_songs_na_count)

taylor_all_songs_na_count <- sapply(taylor_all_songs, function(x) sum(is.na(x)))
print(taylor_all_songs_na_count)

taylor_albums_na_count <- sapply(taylor_albums, function(x) sum(is.na(x)))
print(taylor_albums_na_count)

taylor_album_songs <- taylor_album_songs %>%
  na.omit()

taylor_all_songs <- taylor_all_songs %>%
  na.omit()

taylor_albums <- taylor_albums %>%
  na.omit()
```

Next we will check if data presented by `taylor_album_songs` and `taylor_all_songs` are the same, in case we are missing crucial differences.
```{r}
names(taylor_album_songs) == names(taylor_all_songs)
checking_conflicts_left <- taylor_album_songs %>% anti_join(taylor_all_songs, by = names(taylor_all_songs))
glimpse(checking_conflicts_left)
checking_conflicts_right <- taylor_all_songs %>% anti_join(taylor_album_songs, by = names(taylor_album_songs))
glimpse(checking_conflicts_right)
checking_conflicts_right$album_name %>% unique
```

All the column names match for both tables. There were no non-matching songs in `taylor_album_songs` to `taylor_all_songs`. However, there were 3 albums: "Fearless", "Red" and "The Taylor Swift Holiday Collection", which were found in `taylor_all_songs` but not `taylor_album_songs`.
This means that we should use data from the overarching dataset to give us the widest coverage, hence use `taylor_all_songs`. 
Next, since we will compare receptivity statistics by album, we need to check which albums are present in `taylor_all_songs` and `taylor_albums`.

```{r}
names1 <- taylor_albums %>% select(album_name) %>% unique() %>% arrange(album_name)
names2 <- taylor_all_songs %>% select(album_name) %>% unique() %>% arrange(album_name)

comp_table <- full_join(names1, names2, by = c("album_name"))

combined_table <- rep("No", length(comp_table$album_name))
combined_table <- cbind(combined_table, combined_table)

for (i in 1:length(comp_table$album_name)){
  if (comp_table$album_name[i] %in% names1$album_name) {
    combined_table[i, 1] <- "Yes"
  }
  if (comp_table$album_name[i] %in% names2$album_name) {
    combined_table[i, 2] <- "Yes"
  }
}

combined_table <- cbind(comp_table$album_name, combined_table)
knitr::kable(combined_table, col.names = c("All Albums", "Taylor Albums", "Taylor All Songs"), caption = "Comparison of album names between the tables")
```

Checking the table generated, "The Taylor Swift Holiday Collection" does not appear in `taylor_albums`, thus it will not be considered for receptivity comparison as there is no receptivity data. We will remove that album from `taylor_all_songs`.
```{r removing-The-Taylor-Swift-Holiday-Collection}
taylor_all_songs <- taylor_all_songs %>% filter(album_name != "The Taylor Swift Holiday Collection")
```

To ensure that the visualisation representations are balanced, we will check the range of the various song features in `taylor_all_songs` to see if there is a need to scale the features:
```{r}
# Checking range of values (for all the songs) of numerical variables in taylor_all_songs
ranges_taylor_all_songs <- taylor_all_songs %>%
  ungroup() %>%
  select(danceability:tempo) %>%
  summarise(across(danceability:tempo, ~paste(min(.), "to", max(.))))
glimpse(ranges_taylor_all_songs)

```

From the data dictionary in TidyTuesday, all the features scores except loudness and tempo range from 0 to 1, hence we do not need the scale them.
We are left with loudness and tempo for normalisation. Loudness is measured in decibels, which has a logarithmic scale. To enable a clearer visual representation, we will convert the values of loudness to a linear scale between 0 and 1. 1 represents loudest while 0 represents softest.
We will use min_max scaling for tempo, to fit it into the 0 to 1 scaling in line with the other features (not for direct comparison to the features as range is fixed by us).
```{r}
# Scaling loudness for taylor_all_songs
taylor_all_songs <- taylor_all_songs %>%
  ungroup() %>%
  mutate(loudness = 10^(loudness / 10), tempo = (tempo - min(tempo)) / (max(tempo) - min(tempo))) #%>%
glimpse(taylor_all_songs)
```


### Data engineering
Let's look at the cleaned dataframes for each `taylor_all_songs` and `taylor_albums`.
```{r using-cleaned-datasets}
head(taylor_all_songs, 10)
head(taylor_albums, 10)
```

To compare musical attributes across albums, we will aggregate statistics for each of the musical attributes in each album by taking their mean. Then, we will combine `taylor_all_songs` and `taylor_albums` to tie the receptivity metrics with each common album.
```{r aggregating-statistics}
taylor_album_summary <- taylor_all_songs %>% group_by(album_name) %>% summarise(
  mean_loudness = mean(loudness),
  mean_danceability = mean(danceability),
  mean_liveness = mean(liveness),
  mean_energy = mean(energy),
  mean_mode = round(mean(mode)),
  mean_speechiness = mean(speechiness),
  mean_acousticness = mean(acousticness),
  mean_instrumentalness = mean(instrumentalness),
  mean_valence = mean(valence),
  mean_tempo = mean(tempo)) %>%
  inner_join(taylor_albums, by = c("album_name")) %>%
  relocate(album_release, .after = album_name)
```

Metacritic scores and user scores are representative of the receptivity of the albums because they are the "weighted average" of the albums' individual ratings
from critics and the public respectively (Metacritic, 2023).

While the Metacritic score ranges from 0 to 100 (Metacritic, 2023), the user score has a different range of 0 to 10 which we noticed when exploring the "user reviews" section (Metacritic, n.d.).
We will aggregate these into one statistic, "Receptivity", weighted by their respective ranges. 

Hence we use the following formula: **Receptivity = (metacritic_score + (user_score * 10)) / 2**

```{r creating-Receptivity}
taylor_album_summary <- taylor_album_summary %>% mutate(Receptivity = (metacritic_score + user_score * 10) / 2)
```


## 3. Visualisations and Discussions
### a. What are the most significant features?

#### Methodology
We have chosen to use a density ridge plot to represent the strength values of the song features, less tempo. This will allow us to examine the spread and distribution of values for each feature.
Taller humps and darker colours represent regions of high concentration of values. This plot also allows us to catch potential multi-modal distributions in the features.

#### Plot 1
```{r distribution-plot}
# Defining labels for usage
x_labels <- c("Acousticness", "Danceability", "Energy", "Instrumentalness", "Liveness", "Loudness", "Speechiness", "Valence")

# Convertion to long format for plotting
taylor_long <- taylor_all_songs %>% select(-mode) %>% pivot_longer(danceability:tempo, values_to = "values", names_to = "labels") %>%
  mutate(labels <- as.factor(labels))

ggplot(taylor_long %>% filter(labels != "tempo"), aes(x = values, y = labels, fill = after_stat(density))) +
  geom_density_ridges_gradient(scale = 0.92, rel_min_height = 0.01, show.legend = FALSE) +
  scale_fill_viridis_c(option = "magma", direction = -1) +
  scale_y_discrete(labels = x_labels) +
  theme_minimal() +
  labs(y = "", x = "Feature Strength",
       title = "Distribution Patterns in Musical Features",
       subtitle = "for Swift's Songs") +
  theme(
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 10, hjust = 0),
    axis.title.x = element_text(vjust = -1, size = 10),
    plot.title = element_text(size = 16, hjust = 1.5, face = "bold"),
    plot.subtitle = element_text(hjust = -0.24, face = "bold"),
    aspect.ratio = 1.0,
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_line(color = "lightblue", linewidth = 0.5)
  )
```

#### Discussion
This visualisation helps us pinpoint features with higher variance, which likely contribute more significantly to shifts in Taylor Swift's musical style and potentially her receptivity. 
By identifying features with the widest range (i.e. `valence`, `acousticness`,`energy` and `danceability`), we can see which musical elements vary more across her songs, making her music distinctive.
For example, `valence` shows a broad range with symmetric tails and a central bulge, suggesting a balance of happy and sad songs. 
`Acousticness`, when observed closely, resembles a bimodal distribution with a larger peak at low strength values and another subtle one near the highest strength values, indicating two types of song styles: those that are highly acoustic and those otherwise.
This bimodal distribution implies that Swift maintains clear distinctions between songs that are fully acoustic versus those with a more electronic or produced sound.
Other features, such as `loudness` and `instrumentalness`, are generally lower and more consistent across her songs, highlighting Swift’s preference for vocally driven tracks without heavy instrumental or spoken elements. 
This plot reveals important contrasts but does not show how these features correlate with album receptivity. Hence, we will further explore this in Plot 2.


### b. How have the features we selected influenced Taylor Swift's receptivity?

#### Methodology
We plan to investigate how the selected features with the most variability (from part (a)) might impact Taylor Swift’s receptivity across her career. 
We arranged each album by receptivty to better compare the difference in receptivity with each of the features chosen. Then, we plotted smooth curves from the mean value of each feature for each album to observe the
changes with respect to receptivity. The mean value of each feature is used as an approximate for the average strength of the feature in each album.

Normalised `tempo` is also included here to analyse its changes with respect to her receptivity.
Receptivity is read from the right y-axis while the feature values with normalised tempo are read from the left y-axis. We obtain musical attribute data from `taylor_all_songs` (converted for plotting into `taylor_long`) 
and `receptivity` from `taylor_album_summary`. 

*Disclaimer: Album Numbers reflected in the table and plot do not correspond to actual album numbers. They have been mapped to the Album Names according to the order seen in the plot for ease of reading.*

#### Plot 2
```{r lineplot-dual-axes, fig.width=10, fig.height=4}
taylor_album_plot <- taylor_album_summary %>%
  arrange(Receptivity) %>%
  mutate(rank = row_number(), mean_tempo = mean_tempo - 0.16) %>%
  pivot_longer(mean_loudness: Receptivity, names_to = "labels", values_to = "values") %>%
  mutate(labels = str_remove(labels, "mean_"))

highest_rated_album <- taylor_album_summary %>%
  arrange(desc(Receptivity)) %>%
  head(1) %>%
  pull(Receptivity)


ggplot(taylor_album_plot %>% filter(labels %in% c("acousticness", "valence", "energy", "danceability", "tempo")), aes(x = rank, y = values, color = labels)) +
  geom_smooth(method = "loess",
              se = FALSE,
              formula = y ~ x,
              span = 1.2,
              size = 0.4)  +
  #stat_smooth(se = FALSE, geom = "area",
              #method = "loess", alpha = .1,
              #span = 0.9, aes(fill = labels), show.legend = F) +
  geom_line(data = taylor_album_plot %>% filter(labels == "Receptivity"),
            aes(y = values / 100),
            size = 1, linetype = "solid", lineend = "round") +
  geom_point(data = taylor_album_plot %>% filter(labels == "Receptivity"),
             aes(y = values / 100),
             size = 1) +
  scale_y_continuous(
    name = "Feature Strength (0 - 1)",
    sec.axis = sec_axis(~ . * 100,
                        name = "Receptivity (%)")) + # (Holtz, n.d.)
  labs(title = "Musical Attributes and Receptivity Across \nTaylor Swift Albums",
       x = "Album Number", y = "Feature Values") +
  scale_color_manual(values = c(
                              "tempo" = "brown",
                              "acousticness" = "blue",
                              "valence" = "red",
                              "energy" = "green",
                              "danceability" = "purple",
                              "Receptivity" = "black"),
                    labels = c("Acousticness", "Danceability", "Energy", "Receptivity", "Tempo", "Valence"),
                    name = "Legend",
                    guide  = guide_legend(order = 1)) +
  scale_fill_manual(values = c(
                              "tempo" = "brown",
                              "acousticness" = "blue",
                              "valence" = "red",
                              "energy" = "green",
                              "danceability" = "purple"),
                    guide = "none",
                    labels = c("Acousticness", "Danceability", "Energy", "Tempo", "Valence")) +
  scale_x_continuous(breaks = seq(1, 12, by = 1),  # Custom integer breaks
                     labels = as.character(seq(1, 12, by = 1))) +
  geom_label(aes(label = "Top Album: Red (Taylor's Version)"), x = 4.5, y = 0.95, show.legend = FALSE) +
  annotate("segment", x = 8.3, y = 0.95, xend = 12, yend = highest_rated_album / 100,
           linetype = "dashed", color = "#a13a3a", size = 0.8) +
  geom_point(aes(x = 12, y = highest_rated_album / 100), color = "#d72b2b", size = 7, shape = 1) +
  theme_minimal() +
  theme(legend.position = "right",
  plot.title = element_text(hjust = 0, face = "bold", vjust = 2),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.x = element_line(linetype = "dotted", color = "#b6cee2"),
  axis.line.y.right = element_line(colour = "Black"),
  axis.ticks.y.right = element_line(color = "#2a2929"),
  axis.ticks.length.y.right = unit(.25, "cm"),
  axis.line.y.left = element_line(color = "brown"),
  axis.ticks.y.left = element_line(color = "red"),
  axis.ticks.length.y.left = unit(.25, "cm"),
  aspect.ratio = 0.8)

# Display song names mapped to track numbers
albums_table <- taylor_album_plot %>% select(c("album_name", "rank")) %>% unique()
albumname_tracknumber_table <- cbind(albums_table$rank, albums_table$album_name)
kable(albumname_tracknumber_table,
      col.names = c("Album Number", "Album Songs"),
      caption = "(Taylor Swift Album Names mapped to Album Numbers)")
```

#### Discussion
The plot examines potential correlations between our selected features (i.e. `acousticness`, `valence`, `energy`, `danceability` & `tempo`) and album receptivity by arranging her albums in order of ascending receptivity. 
`Acousticness` tends to be higher in higher-rated albums, while `energy` and `danceability` tend to taper off in strength , suggesting that Swift’s more popular albums lean toward acoustic and introspective qualities.
Despite the wide range of `valence` values observed across Swift's songs in Plot 1, we observed that `valence` strength appears rather stable across albums in this plot. 
Hence, we suggest that `valence` values could be distributed well throughout each album, with a wide range from happy to sad songs.
Additionally, `tempo` appears to be consistent on average across all her albums with minimal change as well, showing that Swift's fans are content with the speed of her songs in general.
`Acousticness` having the most interesting trend deserves some scrutiny. Although Swift's increase in receptivity did not increase proportionately with `acousticness`, it is important to consider that it did not decrease because it shows that her fans were happy with the switch-up.
We think that her audience received this shift well because they were yearning for something different from the usual mainstream pop soundscape of the early 2000s and mid 2010s which is characterised by Electronic Dance music and piercing Disco pop sounds (Savage, 2020). 
To test such a theory, we will be exploring her highest rated album: "Red (Taylor's Version)", to examine the musical makeup of that album based on the four important musical features we picked out in Plot 1. 

### c. What defines a great album (Taylor's Version)?

#### Methodology
To investigate this sub-question, we will examine how each feature varies across the songs in "Red (Taylor's Version)" to guage the rough musical make-up of the album. 
Four bar charts have been plotted for each musical feature, with the bars arranged by the feature's strength values to observe the true range and spread of each feature in the album.

#### Plot 3
```{r faceted-bar-plot}
# Finding her most popular album
highest_rated_album <- taylor_album_summary %>%
  arrange(desc(Receptivity)) %>%
  head(1) %>%
  pull(album_name)

# Filtering the songs from her most popular album
highest_rated_album_songs <- taylor_all_songs %>%
  filter(album_name == highest_rated_album) %>%
  select(album_name, track_number, track_name, danceability, acousticness, energy, valence)

# Reshape the data into long format for plotting
scaled_songs_long <- highest_rated_album_songs %>%
  pivot_longer(cols = danceability:valence,
               names_to = "feature",
               values_to = "value") %>%
  group_by(track_name) %>%
  mutate(total_value = sum(value)) %>%
  ungroup()

# Check the mean value of each feature
feature_mean <- scaled_songs_long %>%
  select(feature, total_value) %>%
  group_by(feature) %>%
  summarise(mean = mean(total_value)) %>%
  arrange(mean) %>%
  pull(feature)

scaled_songs_long <- scaled_songs_long %>%
  arrange(feature, value) %>%
  group_by(feature) %>%
  mutate(new_track_number = row_number())

# Plot with sorted order
ggplot(scaled_songs_long, aes(y = value, x = new_track_number, fill = feature)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ feature, scales = "free_x", labeller = labeller(
    feature = as_labeller(c(
      "acousticness" = "Acousticness",
      "danceability" = "Danceability",
      "energy" = "Energy",
      "valence" = "Valence"
    ))
  )) +
  theme_minimal() +
  labs(title = paste("Distribution of Significant Features of each Song in the \nHighest Rated Album:", highest_rated_album),
       y = "Strength of Features", x = "Songs") +
  theme(
    axis.text.x = element_blank(),
    panel.grid.minor.x = element_line(color = "#addced"),
    plot.title = element_text(size = 12, vjust = 2, face = "bold"),
    plot.subtitle = element_text(size = 8, face = 3),
    aspect.ratio = 0.8,
    axis.title.y.left = element_text(vjust = 2, size = 11)
  ) +
  scale_fill_viridis_d()
```

#### Discussion
In "Red (Taylor's Version)", the varied distribution of features reflects the album's emotional range and dynamic appeal. 
`Acousticness` appears to be highly polarised, echoing the depiction in plot 1, with most songs having lower acousticness strengths but a few with high strength values, providing contrasting listening experiences.
`Danceability` occupies a smaller but moderate range of strength values, indicating a consistent and cohesive rhythm. 
Both `energy` and `valence` span a wide range of values but their distributions are different. Within `energy` it appears that most songs are energetically similar in the upper range with smaller differences in feature strength while a small group of songs have large differences in `energy` within the lower range, creating a rich emotional mix.
Although `valence` appears relatively stable in Plot 2, this plot reveals a broader range within individual songs in a single album. 
This contrast supports our hypothesis in Plot 2 - while albums may average out in terms of emotional tone, Swift maintains a balance of happier and sadder tracks across each album, enhancing their appeal and allowing listeners to experience a more dynamic repertoire.
This blend of moods resonates with listeners who value both sad and happy songs, encapsulating the intricacies of relationships, hence enhancing the album's emotional appeal. 
The critical acclaim of this album also likely means that Taylor Swift will be creating more songs in the future following the same musical palette. We can perhaps anticipate more acoustic songs released alongside commercial tracks to satiate the hunger of her fans. However, music has an ever changing facade.
What was popular last year could be boring this year, hence to predict trends in music is a little whimsical. 
Our analysis of the dataset also highlights this quality of music in how musical features are highly varied across songs from the same artist. However, it is still worth it to study what makes great songs, great.

### Summary of Observed Patterns
Our analysis of Swift’s musical features highlights attributes that may drive her broad appeal. 
High-variance features like acousticness, valence, energy, and danceability indicate a balance of contrasting moods and song styles. 
Notably, highly receptive albums tend to emphasise acoustic qualities over energetic or danceable ones, suggesting that audiences favour this mix of introspective and dynamic elements. 
The consistent presence of emotionally balanced albums suggests a deliberate blend of happy and sad songs that resonates with listeners. 
However, predicting long-term trends in music remains uncertain, as shifts in audience preferences are fluid. 
Still, our analysis offers insights into which musical elements may continue to captivate Swift’s audience.

## 5. Teamwork
Each team member contributed uniquely to the project. 
Timothy focused on data cleaning, writing and editing the introduction and discussion sections, did some source research and assisted with some visualisation plotting.
Robin led the creation and design of the visualisations using ggplot2, selecting appropriate visual styles to illustrate our findings, along with assisting with the search for appropriate sources for the visualisations.
Joel assisted Robin with the continuous editing of the visualisations, identifying issues with each iteration and implementing appropriate changes to improve their styles. 
Zeen Kiat also assisted with the visualisations by supplying appropriate code to work with for illustrate our findings, additionally providing help with the mutation of the original data to fit our needs.
All members collaborated on reviewing and refining the final submission for clarity and cohesion.

## 6. References
Harmon, J. (2023, October 16). Taylor Swift. GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-10-17/readme.md    
Holtz, Y. (n.d.). Dual Y axis with R and ggplot2. The R Graph Gallery – Help and inspiration for R charts. https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html  
Metacritic. (2023). How do you compute METASCORES? Retrieved November 7, 2024, from https://metacritichelp.zendesk.com/hc/en-us/articles/14478499933079-How-do-you-compute-METASCORES  
Metacritic. (n.d.). Taylor Swift by Taylor Swift. https://www.metacritic.com/music/taylor-swift/taylor-swift/user-reviews  
Savage, M. (2020, January 11). Five ways music changed in the 2010s. BBC. https://www.bbc.com/news/entertainment-arts-51061099
