---
title: "DSA2101 Group Project"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidytuesdayR)
library(tidyverse)
library(readr)
library(knitr)
```

# Analysis of Taylor Swift Spotify Data

```{r}
students <- data.frame(
  Group_Members = c("Chua Yong Sheng Joel", "Lim Zeen Kiat", "Robin Ghosh", "Timothy Teo Shao Jun"),
  Matriculation_Number = c("A_", "A_", "A0271671A", "A0272851B")
)

kable(students, col.names = c("Group Members", "Matriculation Number"), 
      caption = "Student Information")
```

=======

## Introduction

(To start on)
Reminders: Define musical attributes (features of the songs) in intro


## Loading Data
```{r}
# Load the Tidy Tuesday datasets for Taylor Swift from Week 42 of 2023
tuesdata <- tidytuesdayR::tt_load(2023, week = 42)

# Extract specific datasets
taylor_album_songs <- tuesdata$taylor_album_songs
taylor_all_songs <- tuesdata$taylor_all_songs
taylor_albums <- tuesdata$taylor_albums

# Save each dataset to CSV files
# write.csv(taylor_album_songs, "taylor_album_songs.csv", row.names = FALSE)
# write.csv(taylor_all_songs, "taylor_all_songs.csv", row.names = FALSE)
# write.csv(taylor_albums, "taylor_albums.csv", row.names = FALSE)
# >>>>>> e3542bd358543883b147a6664c5777a5ed2ce66e
```


## Description of our Data
```{r}
summary(taylor_album_songs)
summary(taylor_all_songs)
summary(taylor_albums)
```

A brief description of the variables relevant to our project is given below:
(To start on)


## Data Cleaning

Start off by filtering for the columns that we want:
```{r}
taylor_album_songs <- taylor_album_songs %>%
    select(album_name, album_release, track_name, danceability, energy, loudness, mode, speechiness, acousticness, instrumentalness, valence, tempo, explicit)

taylor_all_songs <- taylor_all_songs %>%
    select(album_name, album_release, track_name, danceability, energy, loudness, mode, speechiness, acousticness, instrumentalness, valence, tempo, explicit)

taylor_albums <- taylor_albums %>%
    select(!ep)
```

Group by albums:
```{r}
taylor_album_songs <- taylor_album_songs %>%
  group_by(album_name)

taylor_all_songs <- taylor_all_songs %>%
  group_by(album_name)

taylor_albums <- taylor_albums %>%
  group_by(album_name)
```

Checking for NA values in each file:
```{r}
taylor_album_songs_na_count <- sapply(taylor_album_songs, function(x) sum(is.na(x)))
print(taylor_album_songs_na_count)

taylor_all_songs_na_count <- sapply(taylor_all_songs, function(x) sum(is.na(x)))
print(taylor_all_songs_na_count)

taylor_albums_na_count <- sapply(taylor_albums, function(x) sum(is.na(x)))
print(taylor_albums_na_count)
```

There are many occurences of NA data present. Hence, we will need to remove them:
```{r}
taylor_album_songs <- taylor_album_songs %>%
    na.omit()

taylor_all_songs <- taylor_all_songs %>%
    na.omit()

taylor_albums <- taylor_albums %>%
    na.omit()
```

Save cleaned data as new files:
```{r}
write.csv(taylor_album_songs, "CSV files/taylor_album_songs_cleaned.csv", row.names = FALSE)
write.csv(taylor_all_songs, "CSV files/taylor_all_songs_cleaned.csv", row.names = FALSE)
write.csv(taylor_albums, "CSV files/taylor_albums.csv_cleaned", row.names = FALSE)
```


```{r using-cleaned-datasets}
head(taylor_album_songs)
head(taylor_all_songs)
head(taylor_albums)
```

```{r}
names(taylor_album_songs)==names(taylor_all_songs)
checking_conflicts <- taylor_album_songs %>% anti_join(taylor_all_songs, by=names(taylor_all_songs))
head(checking_conflicts)
```

All the column names match for both tables. A tibble of no elements was generated, thus confirming that all rows are present in either tables. Since we can choose which
table we want, we will use taylor_album_songs.

Next, since we are trying to compare popularity statistics by album, we need to check which albums are present in `taylor_album_songs` and `taylor_albums`.

```{r}
names1 <- taylor_albums %>% select(album_name) %>% unique() %>% arrange(album_name)
names2 <- taylor_album_songs %>% select(album_name) %>% unique() %>% arrange(album_name)

comp_table=left_join(names1, names2, by=c("album_name"))

combined_table = rep(NA,length(comp_table$album_name))

for (i in 1:length(names1$album_name) ){
  if (names1$album_name[i] %in% names2$album_name) {
    combined_table[i] <- comp_table$album_name[i]
  }
}

combined_table = cbind(names1$album_name,combined_table)
knitr::kable(combined_table, col.names = c("Taylor Albums","Taylor Album Songs"), caption="Comparison of album names between the tables")
```

Checking the table generated, Fearless and Red do not appear in Taylor Album Songs, thus they will not be considered for popularity comparison.
Next, we will aggregate statistics for each of the musical attributes by taking their mean. Then, we will combine `taylor_album_songs` and `taylor_albums` to tie the popularity metrics with each common album.

```{r aggregating-statistics}
taylor_album_summary <- taylor_album_songs %>% group_by(album_name)%>% summarize(
  mean_loudness = mean(loudness),
  mean_danceability = mean(danceability),
  mean_energy = mean(energy),
  mean_mode = round(mean(mode)),
  mean_speechiness = mean(speechiness),
  mean_acousticness = mean(acousticness),
  mean_instrumentalness = mean(instrumentalness),
  mean_valence = mean(valence),
  mean_tempo = mean(tempo)
) %>% inner_join(taylor_albums, by=c("album_name")) %>% relocate(album_release, .after=album_name)
```

Metacritic scores and User scores are representative of the popularity of the albums because they are averaged ratings of the albums from
critics and the public respectively (Source: NEED SOURCE metacritic.com, another one). 

Metacritic score ranges from 0 to 100 while User Score ranges from 0 to 10. We will aggregate these into one statistic, "Popularity", weighted by their
respective ranges. (Source: NEED SOURCE)

Hence we use the following formula: Popularity = (metacritic_score+(user_score*10))/2

```{r creating-Popularity}
taylor_album_summary <- taylor_album_summary %>% mutate(Popularity = (metacritic_score+user_score*10)/2)
taylor_album_summary[, c(1,2,12)]
```


Exploratory plots: May or may not use, just to select

```{r}
points = lm(data=taylor_album_summary, album_release~Popularity)
ggplot(taylor_album_summary, aes(x=album_release, y=Popularity, color=album_name)) +
  geom_point(size=2) 
```

```{r}
plotting = taylor_album_summary %>% pivot_longer(cols =c(mean_energy, mean_acousticness, mean_instrumentalness, mean_valence), names_to="variable", values_to="value")
ggplot(plotting, aes(x=album_release, y=value, color = variable)) +
  geom_point(size=3) +
  geom_smooth(method="lm") +
  theme_classic()
```

Valence dropped, songs became sadder. Instrumentalness dropped, songs became more vocally driven.
Acousticness increased sharply, songs involved lesser electronic sounds and sounded more raw.
Energy of the tracks have also reduced, further emphasising the mellow trend of her music.
It seems that Taylor Swift aims to be more intimate with her audience. Her popularity has
increased over the years also.