---
title: "DSA2101 Group Project"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
<<<<<<< HEAD

```

## GitHub Documents

Testing! Nullus
This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code
=======

```{r}
library(tidytuesdayR)
library(tidyverse)
library(readr)
```

# Analysis of Taylor Swift Spotify Data
>>>>>>> e3542bd358543883b147a6664c5777a5ed2ce66e

Name                 | Matriculation number
Chua Yong Sheng Joel | A_
Lim Zeen Kiat        | A_
Robin Ghosh          | A0271671A
Timothy Teo Shao Jun | A0272851B

<<<<<<< HEAD
```{r cars}
summary(cars)
```
=======

## Introduction

(To start on)


## Loading Data
```{r}
# Load the Tidy Tuesday datasets for Taylor Swift from Week 42 of 2023
tuesdata <- tidytuesdayR::tt_load(2023, week = 42)

# Extract specific datasets
taylor_album_songs <- tuesdata$taylor_album_songs
taylor_all_songs <- tuesdata$taylor_all_songs
taylor_albums <- tuesdata$taylor_albums

# Save each dataset to CSV files
# write.csv(taylor_album_songs, "taylor_album_songs.csv", row.names = FALSE)
# write.csv(taylor_all_songs, "taylor_all_songs.csv", row.names = FALSE)
# write.csv(taylor_albums, "taylor_albums.csv", row.names = FALSE)
```
>>>>>>> e3542bd358543883b147a6664c5777a5ed2ce66e



<<<<<<< HEAD
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
=======
## Description of our Data
```{r}
summary(taylor_album_songs)
summary(taylor_all_songs)
summary(taylor_albums)
```

A brief description of the variables relevant to our project is given below:
(To start on)


## Data Cleaning

Start off by filtering for the columns that we want:
```{r}
taylor_album_songs <- taylor_album_songs %>%
    select(album_name, album_release, track_name, single_release, loudness, mode, speechiness, acousticness, instrumentalness, valence, tempo)

taylor_all_songs <- taylor_all_songs %>%
    select(album_name, album_release, track_name, single_release, loudness, mode, speechiness, acousticness, instrumentalness, valence, tempo)

taylor_albums <- taylor_albums %>%
    select(!ep)
```

Group by albums:
```{r}
taylor_album_songs <- taylor_album_songs %>% 
  group_by(album_name)

taylor_all_songs <- taylor_all_songs %>%
  group_by(album_name)

taylor_albums <- taylor_albums %>%
  group_by(album_name)
```

Checking for NA values in each file:
```{r}
taylor_album_songs_na_count <- sapply(taylor_album_songs, function(x) sum(is.na(x)))
print(taylor_album_songs_na_count)

taylor_all_songs_na_count <- sapply(taylor_all_songs, function(x) sum(is.na(x)))
print(taylor_all_songs_na_count)

taylor_albums_na_count <- sapply(taylor_albums, function(x) sum(is.na(x)))
print(taylor_albums_na_count)
```

There are many occurences of NA data present. Hence, we will need to remove them:
```{r}
taylor_album_songs <- taylor_album_songs %>%
    na.omit()

taylor_all_songs <- taylor_all_songs %>%
    na.omit()

taylor_albums <- taylor_albums %>%
    na.omit()
```

Save cleaned data as new files:
```{r}
write.csv(taylor_album_songs, "CSV files/taylor_album_songs_cleaned.csv", row.names = FALSE)
write.csv(taylor_all_songs, "CSV files/taylor_all_songs_cleaned.csv", row.names = FALSE)
write.csv(taylor_albums, "CSV files/taylor_albums.csv_cleaned", row.names = FALSE)
```
>>>>>>> e3542bd358543883b147a6664c5777a5ed2ce66e

```{r reading-new-csvs}
taylor_all_songs = read_csv("../CSV files/taylor_all_songs_cleaned.csv")
str(taylor_all_songs)

```